%% ----------------------------------------------------------------
%% REPORT-NAME.tex
%% ----------------------------------------------------------------
\documentclass{src/ecsgdp}
\graphicspath{{./images/}}
\hypersetup{colorlinks=true}
\input{src/definitions}

\usepackage[toc,page]{appendix}
\usepackage{graphicx}
\usepackage{tabto}
\usepackage{color}
\usepackage{lscape}
\usepackage{listings}

\usepackage[hashEnumerators,smartEllipses]{markdown}
%\newcounter{appendixcount}
%\newcommand{\newappendix}[2]{\setcounter{appendixcount}{#1}\addtocounter{appendixcount}{-1}{{#1: #2}}}

%% ----------------------------------------------------------------
\begin{document}
\frontmatter
\title      {Wireless Telemetry Pipelines and Localising ML Technologies\\}
\authors	{
{Anurag Sahare}\\
{Eu Jin Ong}\\
{Nazatul Syuhada Mohd Amran}\\
{Akshay Sudarsanan Nair}\\
}
\addresses  {\groupname\\\deptname\\\univname}
\date       {January, 2021}
\subject    {}
\keywords   {}
\supervisor {Dr Mohammed El-Hajar}
\examiner   {Dr Michael Ng}
\degree     {Master of Engineering}
\reporttype {Group Design Project Report} % Change here if you're doing a 3YP report
\maketitle

\begin{abstract}
\include{pages/0_Abstract}
\end{abstract}
\acknowledgements{First of all, the team would like to thank our project supervisor Dr. Mohammed El-Hajjar for providing us with continued guidance and instrumental support throughout the duration of this project. Dr El-Hajjar ensured the project was progressed in a timely manner and helped build a healthy working relationship between the team and the external partner InterDigital. 

We would also like to express our sincere gratitude to the InterDigital supervisor Mr. Filipe Conceicao without whom this project would not be a success. Mr. Conceicao provided the team with invaluable knowledge and guidance, as well as working tirelessly alongside the team to ensure project expectations were met. Moreover, he made himself available at all times with little to no notice to provide the team with his expertise and assistance, along with helping solve any minor and major issues faced. For this the team cannot thank Mr. Conceicao enough. 

Lastly, from InterDigital we would like to thank Ibrahim Hemadeh, Tezcan Cogalan and Alain Mourad all of whom assisted the team during critical stages of the project development.}
%Let me know when you've finished the ISA%
\tableofcontents
\listoffigures
\listoftables
\lstlistoflistings

%% ----------------------------------------------------------------
% Optional extra pages
% \listofsymbols{ll}{$w$ & The weight vector}

% \dedicatory{To \dots}
%% ----------------------------------------------------------------

% \mainmatter means that we've gone from i, ii, iii, iv, v etc. introduction
% numbering to 1,2,3,4,5 chapter numbering

\mainmatter

\include{pages/1_Introduction}
\include{pages/2_Chapter2}
\include{pages/3_Chapter3}
\include{pages/4_Chapter4}
\include{pages/5_Chapter5}
\include{pages/6_Chapter6}
\include{pages/7_Chapter7}
\include{pages/8_Chapter8}
%\include{pages/9_Conclusions}
%\include{pages/9_Conclusions}
% include acknowledgements
% \backmatter means that we've gone from 1,2,3,4,5 chapter numbering
% to unnumbered bibliography/appendices.
% \backmatter

\bibliographystyle{src/IEEEtran}
\bibliography{master}
% \appendix
\begin{appendices}
\include{pages/99_Appendix}
\include{pages/appendixB}
\include{pages/appendixC}
\include{pages/appendixD}
\include{pages/appendixE}
\include{pages/appendixF}
\include{pages/appendixG}
\end{appendices}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
